Field-informed Reinforcement Learning for Learning Large Scale Collective Tasks

### 2023-05-05 paper.tex
chore: shrink marl section removing DecPOMPD discussion

\subsection{Problem definition}

@@

One interesting application of \ac{RL} is when there are multiple learning agents involved. 
 Such scenarios are referred to as multi-agent reinforcement learning (MARL)~\cite{zhang2019marl}. 
 While standard \ac{RL} approaches use Markov decision processes to model the world, 
 in MARL for distributed systems, the notion of 
 \acp{DecPOMDP}~\cite{Decpomdp2000} is used.

A \ac{DecPOMDP} represents a sequential game, 
 in which each agent receives a local observation about the world they 
 inhabit and receives a joint immediate reward in response to the actions they take. 
% 
\ga{Improve, if necessary, the following paragraph.}
Formally, a \ac{DecPOMDP} is defined as a tuple $\langle N, S, \{A_i\}, P, R, \{\Omega_i\}, O, \gamma \rangle$, 
 where $N$ is the total number of agents that live in the environment, 
 $S$ is the state set of the environment, 
 $\{A_i\}$ is the set of actions for agent $i$ and $A$ is the joint action space, 
 $P$ is the probability transition function, 
 $R$ is the immediate joint reward function, and 
 $\{\Omega_i\}$ is the set observation function for the agent $i$,
 $O$ is the observation space, and finally $\gamma$ is the discount factor.
%
On top of this model, each agent tries to learn a policy $\pi_i$ in order 
 to maximise the long-term joint reward signal.
In the case of some of these concepts, 
 there are several approaches/classifications in the literature, 
 like cooperative (i.e., the reward function incentivizes collective outcomes)
 heterogeneous (i.e., the agents have different action spaces and policies) and
 homogenous (i.e., the agents have the same action space and policy) settings.
%  
In particular, in this work, we consider homogenous many agent RL~\cite{yang2021many}, 
 where $N \gg 2$ and each agent is interchangeable and indistinguishable.
%
This research area is relevant in the context of large-scale systems 
 when the incentive of the individual is reduced compared to the collective behaviour of the system, 
 which is found in collective adaptive systems such as swarm robotics.

>>>>

\subsection{System definition}

@@

One interesting application of \ac{RL} is when there are multiple learning agents involved. 
 Such scenarios are referred to as multi-agent reinforcement learning (MARL)~\cite{zhang2019marl}. 
% While standard \ac{RL} approaches use Markov decision processes to model the world, 
% in MARL for distributed systems, the notion of 
% \acp{DecPOMDP}~\cite{Decpomdp2000} is used.
%
%A \ac{DecPOMDP} represents a sequential game, 
% in which each agent receives a local observation about the world they 
% inhabit and receives a joint immediate reward in response to the actions they take. 
% 
%\ga{Improve, if necessary, the following paragraph.}
%Formally, a \ac{DecPOMDP} is defined as a tuple $\langle N, S, \{A_i\}, P, R, \{\Omega_i\}, O, \gamma \rangle$, 
% where $N$ is the total number of agents that live in the environment, 
% $S$ is the state set of the environment, 
% $\{A_i\}$ is the set of actions for agent $i$ and $A$ is the joint action space, 
% $P$ is the probability transition function, 
% $R$ is the immediate joint reward function, and 
% $\{\Omega_i\}$ is the set observation function for the agent $i$,
% $O$ is the observation space, and finally $\gamma$ is the discount factor.
%
%On top of this model, each agent tries to learn a policy $\pi_i$ in order 
% to maximise the long-term joint reward signal.
%In the case of some of these concepts, 
% there are several approaches/classifications in the literature, 
% like cooperative (i.e., the reward function incentivizes collective outcomes)
% heterogeneous (i.e., the agents have different action spaces and policies) and
% homogenous (i.e., the agents have the same action space and policy) settings.
%  
In particular, in this work, we consider homogenous many agent RL~\cite{yang2021many}, 
 where $N \gg 2$ and each agent is interchangeable and indistinguishable.
%
This research area is relevant in the context of large-scale systems 
 when the incentive of the individual is reduced compared to the collective behaviour of the system, 
 which is found in collective adaptive systems such as swarm robotics.
